---
output: github_document
---

# Roche affaliated hex stickers

Projects where we are involved. To add one, make sure to add your hex under the format `EXACT_PACKAGE_NAME.png` to the PNG 
folder at a minumum (if you have a svg, please also add it there). The readme is updated on your PR.

```{r, echo = FALSE, message = FALSE}
library(magick)
logos <- tools::file_path_sans_ext(dir("PNG", pattern = "\\.png$"))
png <- paste0("PNG/", logos, ".png")
svg <- paste0("SVG/", logos, ".svg")
thumb <- paste0("thumbs/", logos, ".png")
resize <- function(path_in, path_out) {
  image <- image_read(path_in)
  image <- image_resize(image, "278x")
  image_write(image, path_out)
}
outdated <- !file.exists(thumb) | file.mtime(thumb) < file.mtime(png)
invisible(Map(resize, png[outdated], thumb[outdated]))
```

```{r, results = "asis", echo = FALSE}
img <- glue::glue('<img alt="Logo for {logos}" src="{thumb}" width="139" height="139">')
png_link <- glue::glue('<a href="{png}">{logos}.png</a>')
#svg_link <- glue::glue('<a href="{svg}">{logos}.svg</a>')
cell <- paste0(
  "<td>", img, "<br />", 
  png_link, "<br />", 
  #svg_link, 
  "</td>")
cols <- 4
rows <- ceiling(length(cell) / cols)
row_id <- rep(seq_len(rows), each = cols, length.out = length(cell))
row_cells <- split(cell, row_id)
cat("<table>\n")
cat(paste0("<tr>", sapply(row_cells, paste, collapse = ""), "</tr>"), sep = "")
cat("</table>\n")
```

# Acknowledgements

Code for this repo has been forked from `rstudio/hex-stickers`. Copyright of the images is defined by the sourced project (see source repo for hex-sticker)
